%++++++++++++++++++++++++++++++++++++++++
% Don't modify this section unless you know what you're doing!
\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{graphicx} % takes care of graphic including machinery
\graphicspath{ {./images/} }
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage{float}
\usepackage{textcomp}
\usepackage{amsmath}
%++++++++++++++++++++++++++++++++++++++++


\begin{document}

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	
	\center % Centre everything on the page
	
	%------------------------------------------------
	%	Headings
	%------------------------------------------------
	
	\textsc{\LARGE Advanced User Interface}\\[0.5cm] % Main heading such as the name of your university/college
	
	\textsc{\Large 2018/19}\\[0.5cm] % Major heading such as course name
	
	%------------------------------------------------
	%	Title
	%------------------------------------------------
	
	\HRule\\[0.4cm]
	
	{\huge\bfseries Public speech in Virtual Reality\\SpeechVR}\\[0.4cm] % Title of your document
	
	\HRule\\[1cm]
	
	
	\large\textit{Author}\\[0.3cm]
	Alberto Patti\\
	Yu Zhu\\[1.5cm]
	

	\begin{abstract}
	This project offers people that have fear of speaking in public an instrument that allows them to try their speech in a virtual environment. This basic idea is expanded by using a biosensor to manipulate the environment the user is put in: the amount of people that the user sees in the audience changes based on the anxiety level determined by reading the values from the biosensor.
	\end{abstract}
\end{titlepage}

\tableofcontents
\pagebreak
\section{Introduction}
	\input{Files/Introduction.tex}
	\pagebreak

\section{NGR}
	\input{Files/NGR.tex}
	\pagebreak
	
\section{State of the art}
	\input{Files/StateOfTheArt.tex}
	\pagebreak
	
\section{UX design}
	\input{Files/UXDesign.tex}
	\pagebreak
	
\section{Implementation}
	\input{Files/Implementation.tex}
	\pagebreak
	
\section{Value proposition}
	\input{Files/ValueProposition.tex}
	\pagebreak

\section{Future work}
	\input{Files/FutureWork.tex}
	\pagebreak


%++++++++++++++++++++++++++++++++++++++++
% References section will be created automatically 
% with inclusion of "thebibliography" environment
% as it shown below. See text starting with line
% \begin{thebibliography}{99}
% Note: with this approach it is YOUR responsibility to put them in order
% of appearance.

\begin{thebibliography}{99}

\bibitem{model}
Rapee, R. M., \& Heimberg, R. G. (1997). A cognitive-behavioral model of anxiety in social phobia. Behaviour research and therapy, 35(8), 741-756.

\bibitem{VRPublicSpeaking}
Slater, M., Pertaub, D. P., \& Steed, A. (1999). Public speaking in virtual reality: Facing an audience of avatars. IEEE Computer Graphics and Applications, 19(2), 6-9.

\bibitem{VRPublicSpeaking2}
Pertaub, D. P., Slater, M., \& Barker, C. (2002). An experiment on public speaking anxiety in response to three different types of virtual audience. Presence: Teleoperators \& Virtual Environments, 11(1), 68-78.

\bibitem{VRPublicSpeaking3}
Chollet, M., Sratou, G., Shapiro, A., Morency, L. P., \& Scherer, S. (2014, May). An interactive virtual audience platform for public speaking training. In Proceedings of the 2014 international conference on Autonomous agents and multi-agent systems (pp. 1657-1658). International Foundation for Autonomous Agents and Multiagent Systems.

\bibitem{VRPublicSpeaking4}
Poeschl, S., \& Doering, N. (2012, March). Virtual training for Fear of Public Speaking—Design of an audience for immersive virtual environments. In Virtual Reality Short Papers and Posters (VRW), 2012 IEEE (pp. 101-102). IEEE.

\bibitem{VRPublicSpeaking5}
McKinney, M. E., Gatchel, R. J., \& Paulus, P. B. (1983). The effects of audience size on high and low speech-anxious subjects during an actual speaking task. Basic and Applied Social Psychology, 4(1), 73-87.

\bibitem{breathing}
Bernardi, L., Wdowczyk-Szulc, J., Valenti, C., Castoldi, S., Passino, C., Spadacini, G., \& Sleight, P. (2000). Effects of controlled breathing, mental activity and mental stress with or without verbalization on heart rate variability. Journal of the American College of Cardiology, 35(6), 1462-1469.
\end{thebibliography}


\end{document}